### Student Name: Fill in the blank.
### Class : STA 32 Winter 2015
### Homework Solutions/Template 6


###Problem 1
```{r,echo = FALSE}
Conf.Int = function(X,alpha){
  n = length(X)
  x.bar = mean(X)
  s.e = sd(X)/sqrt(n)
  Z.val = qnorm(0.05/2,lower.tail = FALSE) 
  t.val = qt(0.05/2,df = n-1,lower.tail = FALSE) 
  Z.conf.int = x.bar +c(-1,1)*Z.val*s.e
  t.conf.int = x.bar +c(-1,1)*t.val*s.e
  both.int = matrix(c(Z.conf.int,t.conf.int),byrow = TRUE,nrow = 2)
  colnames(both.int) = c("Lower Bound","Upper Bound")
  rownames(both.int) = c("Z CI","t CI")
  return(both.int)
}
```
+ (a)
The confidence intervals are:
```{r, echo = FALSE}
Conf.Int(X = rnorm(15, mean = 5, sd = 3), alpha = 0.05)
```
+ (b)
The confidence intervals are:
```{r, echo = FALSE}
Conf.Int(X = rexp(15,rate = 1/5), alpha = 0.05)
```
+ (c)
The confidence intervals are:
```{r, echo = FALSE}
Conf.Int(X = rnorm(50, mean = 5, sd = 3), alpha = 0.05)
```
+ (d)
The confidence intervals are:
```{r, echo = FALSE}
Conf.Int(X = rexp(50,rate = 1/5), alpha = 0.05)
```
###Problem 2
```{r,echo = FALSE}
C.I.cover = function(ThePop,alpha,n,N,TrueMean){
  all.T.F = sapply(1:N,function(i){
    Sample = sample(ThePop,n,replace = FALSE)
    C.I = Conf.Int(Sample, alpha = alpha)
    Z.cover = ifelse(C.I[1,1] <= TrueMean & C.I[1,2] >= TrueMean,TRUE,FALSE)
    t.cover = ifelse(C.I[2,1] <= TrueMean & C.I[2,2] >= TrueMean,TRUE,FALSE)
    cover = matrix(c(Z.cover,t.cover),nrow = 1)
    colnames(cover) = c("Z-coverage","t-coverage")
    return(cover)
  })
  all.T.F = t(all.T.F)
  cover.proportion = colMeans(all.T.F)
  return(cover.proportion)
}
```
+ (a)
The proportion of confidence intervals covering the true mean can be found below:
```{r, echo = FALSE}
C.I.cover(ThePop = rnorm(10000,mean = 5, sd = 3),alpha = 0.05, n = 15, N = 10000,TrueMean = 5)
```
+ (b)
The proportion of confidence intervals covering the true mean can be found below:
```{r, echo = FALSE}
C.I.cover(ThePop = rexp(10000,rate = 1/5),alpha = 0.05, n = 15, N = 10000,TrueMean = 5)
```
+ (c)
The proportion of confidence intervals covering the true mean can be found below:
```{r, echo = FALSE}
C.I.cover(ThePop = rnorm(10000,mean = 5, sd = 3),alpha = 0.05, n = 50, N = 10000,TrueMean = 5)
```
+ (d)
The proportion of confidence intervals covering the true mean can be found below:
```{r, echo = FALSE}
C.I.cover(ThePop = rexp(10000,rate = 1/5),alpha = 0.05, n = 50, N = 10000,TrueMean = 5)
```
+ (e) The t-distribution coverage is better than the z-distribution coverage.  This is most likely because n is small, and when n is small we assume that we have made a larger error and should use a t distribution.

+ (f) While both are below the theorectical 0.95, the t-distribution still outperforms the z-distribution.  This is because the t-distribution is more conservative, and results in wider confidence intervals.

+ (g) Here the t-distribution and z-distribution perform about the same.  This is because in this case n is large, and the population is normal, so we should expect little improvement with t.

+ (h) The t-distribution outperforms the z-distribution in this case.  Even though n is large, when the population is not normal, it is often a better idea to select the more conservative interval.