### Student Name: Fill in the blank.
### Class : STA 32 Winter 2015
### Homework Solutions/Template 2


1. Problem 1
```{r, echo = FALSE}
PairFunction = function(n, part = "a"){
  CardValue = rep(c("A",2:10,"J","Q","K"),times = 4)
  CardSuit = rep(c("S","C","H","D"), each = 13)
  CardDeck = t(rbind(CardValue,CardSuit))
  ManyTwoCards = sapply(1:n,function(i){
    TwoCards = CardDeck[sample(1:52,2,replace = FALSE),]
    if(part == "a"){
      CheckCondition = ifelse(TwoCards[1,1] == TwoCards[2,1], TRUE,FALSE)
      return(CheckCondition)
    }else if(part == "b"){
      CheckCondition = ifelse((TwoCards[1,2] == "H") & (TwoCards[2,2] == "H"), TRUE,FALSE)
      return(CheckCondition)    
    }else if(part == "c"){
      CheckSuit = ifelse(sum(TwoCards[,2] %in% c("H","D") ) == 2, TRUE, FALSE)
      CheckValue = ifelse(TwoCards[1,1] == TwoCards[2,1], TRUE,FALSE)
      CheckCondition = ifelse(CheckSuit + CheckValue == 2, TRUE, FALSE)
      return(CheckCondition)      
    }else if(part == "all"){
      a.Condition = ifelse(TwoCards[1,1] == TwoCards[2,1], TRUE,FALSE)
      b.Condition = ifelse(TwoCards[1,2] == TwoCards[2,2], TRUE,FALSE)
      c.Suit = ifelse(sum(TwoCards[,2] %in% c("H","D") ) == 2, TRUE, FALSE)
      c.Condition = ifelse(c.Suit + a.Condition == 2, TRUE, FALSE)
      return(c(a.Condition, b.Condition,c.Condition))
    }else{
      stop("Error, definition of parameter :part: unknown")
    }
  })
  if(part != "all"){
    TheProbability  = round(sum(ManyTwoCards)/n,digits = 4)
    return(TheProbability)
  }else{
    TheProbability  = round(rowSums(ManyTwoCards)/n,digits = 4)
    names(TheProbability) = c("Part(a)","Part(b)","Part(c)")
    print(TheProbability)
    return(TheProbability)
  }
}
```
+ (a): The probability of getting two cards of the same value if you draw two cards for the specified **n**'s are:
```{r,echo = FALSE}
Results = sapply(c(100,1000,10000,100000),function(i){
  PairFunction(i,"a")
})
names(Results) = as.character(c(100,1000,10000,100000))
Results
#Note, by math it is 
MathProb = (52/52)*(3/51)
```

+ (b): The probability of getting two cards hearts if you draw two cards for the specified **n**'s are:
```{r,echo = FALSE}
Results = sapply(c(100,1000,10000,100000),function(i){
  PairFunction(i,"b")
})
names(Results) = as.character(c(100,1000,10000,100000))
Results
#Note, by math it is 
MathProb = (13/52)*(12/51)
```

+ (c): The probability of getting two cards of the same value where one is a heart and the other a diamond if you draw two cards for the specified **n**'s are:
```{r,echo = FALSE}
Results = sapply(c(100,1000,10000,100000),function(i){
  PairFunction(i,"c")
})
names(Results) = as.character(c(100,1000,10000,100000))
Results
#Note, by math it is 
MathProb = (26/52)*(1/51)
```

2. Problem 2:  The results for the various probabilities with the various **n**'s are:

```{r,echo = FALSE}
BiasedCoin = function(n){
  Color = sample(c("R","G","B"),n,replace = TRUE)
  Flip = sapply(1:n,function(i){
  if(Color[i] =="R"){
  return(sample(c("T","H"),1,prob = c(0.60,0.40)))
  }else if(Color[i] =="B"){
  return(sample(c("T","H"),1,prob = c(0.30,0.70)))
  }else if(Color[i] == "G"){
  return(sample(c("T","H"),1,prob = c(0.50,0.50)))
  }else{print("Error")}
  })
  P.A = sum(Color == "B")/n
  P.B = sum(Flip =="H")/n
  P.AorB = sum(Flip =="H" |Color == "B")/n
  P.ACorB = sum(Flip =="H" |Color != "B")/n
  P.AandB = sum(Flip =="H" & Color == "B")/n
  P.AgB = sum(Flip =="H" & Color == "B")/sum(Flip == "H")
  P.AgBc = sum(Flip !="H" & Color == "B")/sum(Flip != "H")
  Results = matrix(c(P.A,P.B,P.AorB,P.ACorB,P.AandB,P.AgB,P.AgBc),nrow = 1)
  colnames(Results)= c("P(A)","P(B)","P(AUB)","P(AcUB)","P(A&B)","P(A|B)","P(A|Bc)")
  return(Results)
}
```

+ n = 100: 
```{r, echo = FALSE}
BiasedCoin(100)
```

+ n = 1000: 
```{r, echo = FALSE}
BiasedCoin(1000)
```

+ n = 10000: 
```{r, echo = FALSE}
BiasedCoin(10000)
```

+ n = 100000: 
```{r, echo = FALSE}
BiasedCoin(100000)
```
3. Problem 3
The results for the various probabilities with the various **n**'s are:
```{r, echo = FALSE}
Damaged = function(n){
  WhatSector = sample(c("Allocation Only","Non-Essential Only","Both"),n,replace = TRUE,prob = c(.2,.7,.1))
  PartA = sum(WhatSector == "Allocation Only" | WhatSector == "Both")/length(WhatSector)
  PartB = sum(WhatSector == "Non-Essential Only" | WhatSector == "Both")/length(WhatSector)
  PartC = sum(WhatSector == "Both")/sum(WhatSector == "Allocation Only" | WhatSector == "Both")
  PartD = sum(WhatSector == "Both")/sum(WhatSector == "Non-Essential Only" | WhatSector == "Both")
   PartE = sum(WhatSector == "Allocation Only")/sum(WhatSector == "Allocation Only" | WhatSector == "Both")
  PartF = sum(WhatSector == "Non-Essential Only")/sum(WhatSector == "Non-Essential Only" | WhatSector == "Both")
  Results = c(PartA,PartB,PartC,PartD,PartE,PartF)
  names(Results) = c("Part A","Part B","Part C","Part D","Part E","Part F")
  return(Results)
}
```
+ n = 100: 
```{r, echo = FALSE}
Damaged(100)
```

+ n = 1000: 
```{r, echo = FALSE}
Damaged(1000)
```

+ n = 10000: 
```{r, echo = FALSE}
Damaged(10000)
```

+ n = 100000: 
```{r, echo = FALSE}
Damaged(100000)
```
********
### Code Appendix 
```
###Problem 1
PairFunction = function(n, part = "a"){
  CardValue = rep(c("A",2:10,"J","Q","K"),times = 4)
  CardSuit = rep(c("S","C","H","D"), each = 13)
  CardDeck = t(rbind(CardValue,CardSuit))
  ManyTwoCards = sapply(1:n,function(i){
    TwoCards = CardDeck[sample(1:52,2,replace = FALSE),]
    if(part == "a"){
      CheckCondition = ifelse(TwoCards[1,1] == TwoCards[2,1], TRUE,FALSE)
      return(CheckCondition)
    }else if(part == "b"){
      CheckCondition = ifelse(TwoCards[1,2] == TwoCards[2,2], TRUE,FALSE)
      return(CheckCondition)    
    }else if(part == "c"){
      CheckSuit = ifelse(sum(TwoCards[,2] %in% c("H","D") ) == 2, TRUE, FALSE)
      CheckValue = ifelse(TwoCards[1,1] == TwoCards[2,1], TRUE,FALSE)
      CheckCondition = ifelse(CheckSuit + CheckValue == 2, TRUE, FALSE)
      return(CheckCondition)      
    }else if(part == "all"){
      a.Condition = ifelse(TwoCards[1,1] == TwoCards[2,1], TRUE,FALSE)
      b.Condition = ifelse(TwoCards[1,2] == TwoCards[2,2], TRUE,FALSE)
      c.Suit = ifelse(sum(TwoCards[,2] %in% c("H","D") ) == 2, TRUE, FALSE)
      c.Condition = ifelse(c.Suit + a.Condition == 2, TRUE, FALSE)
      return(c(a.Condition, b.Condition,c.Condition))
    }else{
      stop("Error, definition of parameter :part: unknown")
    }
  })
  if(part != "all"){
    TheProbability  = round(sum(ManyTwoCards)/n,digits = 4)
    return(TheProbability)
  }else{
    TheProbability  = round(rowSums(ManyTwoCards)/n,digits = 4)
    names(TheProbability) = c("Part(a)","Part(b)","Part(c)")
    print(TheProbability)
    return(TheProbability)
  }
}
#Part a
Results = sapply(c(100,1000,10000,100000),function(i){
  PairFunction(i,"a")
})
names(Results) = as.character(c(100,1000,10000,100000))
Results
#Part b
Results = sapply(c(100,1000,10000,100000),function(i){
  PairFunction(i,"b")
})
names(Results) = as.character(c(100,1000,10000,100000))
Results
#Part c
Results = sapply(c(100,1000,10000,100000),function(i){
  PairFunction(i,"c")
})
names(Results) = as.character(c(100,1000,10000,100000))
Results

###Problem 2
BiasedCoin = function(n){
  Color = sample(c("R","G","B"),n,replace = TRUE)
  Flip = sapply(1:n,function(i){
  if(Color[i] =="R"){
  return(sample(c("T","H"),1,prob = c(0.60,0.40)))
  }else if(Color[i] =="B"){
  return(sample(c("T","H"),1,prob = c(0.30,0.70)))
  }else if(Color[i] == "G"){
  return(sample(c("T","H"),1,prob = c(0.50,0.50)))
  }else{print("Error")}
  })
  P.A = sum(Color == "B")/n
  P.B = sum(Flip =="H")/n
  P.AorB = sum(Flip =="H" |Color == "B")/n
  P.ACorB = sum(Flip =="H" |Color != "B")/n
  P.AandB = sum(Flip =="H" & Color == "B")/n
  P.AgB = sum(Flip =="H" & Color == "B")/sum(Flip == "H")
  P.AgBc = sum(Flip !="H" & Color == "B")/sum(Flip != "H")
  Results = matrix(c(P.A,P.B,P.AorB,P.ACorB,P.AandB,P.AgB,P.AgBc),nrow = 1)
  colnames(Results)= c("P(A)","P(B)","P(AUB)","P(AcUB)","P(A&B)","P(A|B)","P(A|Bc)")
  return(Results)
}
BiasedCoin(100)
BiasedCoin(1000)
BiasedCoin(10000)
BiasedCoin(100000)
### Problem 3
Damaged = function(n){
  WhatSector = sample(c("Allocation Only","Non-Essential Only","Both"),n,replace = TRUE,prob = c(.2,.7,.1))
  PartA = sum(WhatSector == "Allocation Only" | WhatSector == "Both")/length(WhatSector)
  PartB = sum(WhatSector == "Non-Essential Only" | WhatSector == "Both")/length(WhatSector)
  PartC = sum(WhatSector == "Both")/sum(WhatSector == "Allocation Only" | WhatSector == "Both")
  PartD = sum(WhatSector == "Both")/sum(WhatSector == "Non-Essential Only" | WhatSector == "Both")
   PartE = sum(WhatSector == "Allocation Only")/sum(WhatSector == "Allocation Only" | WhatSector == "Both")
  PartF = sum(WhatSector == "Non-Essential Only")/sum(WhatSector == "Non-Essential Only" | WhatSector == "Both")
  Results = c(PartA,PartB,PartC,PartD,PartE,PartF)
  names(Results) = c("Part A","Part B","Part C","Part D","Part E","Part F")
  return(Results)
}
Damaged(100)
Damaged(1000)
Damaged(10000)
Damaged(100000)
```
