\documentclass[12pt,letterpaper]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{cancel}
\usepackage[margin=1in]{geometry}
\usepackage{titling}
\usepackage{textcomp}

\setlength{\droptitle}{-10ex}

\preauthor{\begin{flushright}\large \lineskip 0.5em}
\postauthor{\par\end{flushright}}
\predate{\begin{flushright}\large}
\postdate{\par\end{flushright}}

\title{PHIL 112 Homework 1\vspace{-2ex}}
\author{Hardy Jones\\
        999397426\\
        Dr. Landry\vspace{-2ex}}
\date{Winter 2014}

\begin{document}
  \maketitle

  \begin{enumerate}
    \item
      Specify the atomic formulas of PL.

      Every expression of PL that is either a sentence letter of PL, or
      an $n$-place predicate of PL followed by $n$ individual terms of PL is an atomic formula of PL.

    \item
      Give the recursive definition of `formula of PL'.

      \begin{enumerate}
        \item Every atomic formula \textbf{P} is a formula of PL.
        \item If \textbf{P} is a formula of PL, then so is $\neg$\textbf{P}.
        \item If \textbf{P} and \textbf{Q} are formulae of PL,
          then so are \textbf{P}$\land$\textbf{Q}, \textbf{P}$\lor$\textbf{Q},
          \textbf{P}$\supset$\textbf{Q}, and \textbf{P}$\equiv$\textbf{Q}.
        \item If \textbf{P} is a formula of PL that contains at least one occurrence of \textbf{x} and no \textbf{x}-quantifier,
          then $\forall$\textbf{xP} and $\exists$\textbf{xP} are formulae of PL.
        \item Nothing else is a formula of PL unless it can be made from the previous rules.
      \end{enumerate}

    \item
      Indicate which of the following are formulas of PL, and which of those are sentences of PL.

      \begin{enumerate}
        \item
          Quantified Formula of PL.

          Not a Sentence of PL since the subformula has a quantified x.

          \underline{($\forall$x)}[Fxa $\supset$ ($\forall$x)Gax]
        \item
          Truth-functionally compound Formula of PL and Sentence of PL.

          ($\forall$z)Fza \underline{$\supset$} $\neg$($\exists$z)Gaz
        \item
          Truth-functionally compound Formula of PL and Sentence of PL.

          \underline{$\neg$}($\forall$y)Gyy
        \item
          Truth-functionally compound Formula of PL.

          Not a sentence of PL for the subformula has at least one free variable.

          Faz \underline{$\supset$} ($\forall$x)Fxa
        \item
          Not a formula of PL for there is no x in Fab.

          $\neg$($\exists$x)Fab
      \end{enumerate}

    \item
      List all the sub-formulas of each of the following:

      \begin{tabular}{l l}
        formula & subformulae \\
        \hline
        ($\forall$x)[($\exists$y)Fxy $\supset$ Gax] & ($\forall$x)[($\exists$y)Fxy $\supset$ Gax] \\
        & ($\exists$y)Fxy $\supset$ Gax \\
        & ($\exists$y)Fxy \\
        & Fxy \\
        & Gax \\

        $\neg$ Fab $\equiv$ ($\forall$x) $\neg$ Fxb & $\neg$ Fab $\equiv$ ($\forall$x) $\neg$ Fxb \\
        & $\neg$ Fab \\
        & Fab \\
        & ($\forall$x) $\neg$ Fxb \\
        & $\neg$ Fxb \\
        & Fxb \\
      \end{tabular}

    \item
      Symbolize English sentences a-d in PL,
      and give English readings for e-h

      \begin{enumerate}
        \item ($\forall$x)(Tx $\supset$ Ux)
        \item ($\forall$x)(Tx $\supset$ $\neg$ Ux)
        \item ($\exists$x)(Tx $\land$ $\neg$ Ux)
        \item ($\exists$x)(Tx $\land$ Ux)
        \item Sarah likes all brown toads.
        \item Some brown toads like Sarah but not all brown toads like Sarah.
        \item Sarah likes all toads if and only if they are brown.
        \item Sarah does not like any toads and no toads like Sarah.
      \end{enumerate}

    \item
      Symbolize a-d in PL and give English readings of e-h.
      \begin{enumerate}
        \item Ccs $\land$ ($\exists$x)((Fx $\land$ Gx) $\land$ Csx)
        \item $\neg$ ($\exists$x)[Fx $\land$ ($\forall$y)(Ty $\supset$ Lxy)]
        \item ($\forall$x)[($\forall$y)[(Fx $\land$ Ty) $\supset$ $\neg$Lxy]]
        \item ($\forall$x)[(Fx $\land$ Lsx) $\supset$ ($\forall$y)(Ty $\supset$ Lyx)]

        \item No frog likes any toad.
        \item There exists at least one frog that is liked by all toads.
        \item All green frogs like all brown toads.
        \item Every toad that is liked by at least one frog is liked by Sarah.
      \end{enumerate}

    \item
      Indicate which of the listed expressions are substitution instances of:

      `($\exists$x) $\neg$ ($\forall$w) $\neg$ Mwx'

      \begin{enumerate}
        \item Substitution
        \item Substitution
        \item Not a substitution
        \item Substitution
      \end{enumerate}

    \item
      Using the symbolization key given below,
      symbolize English sentences a-c in PLE,
      and give English readings of d-f.

      \begin{enumerate}
        \item Pa $\land$ Pf(a)
      \end{enumerate}
  \end{enumerate}
\end{document}
